Introducing ICBe: Supplementary Information

### 2022-10-24 replication_paper/psrm_draft/ICBe_political_analysis_submission_rmd.Rmd
psrm prep

ft_cuba_precision %>% save_as_image(path=here::here("replication_paper","political_analysis_draft","case_study_cuban_precision.png"), zoom=1) # webshot = "webshot2"
temp <- NULL

@@

bands=which( 1:nrow(lit_review_alt) %% 2 == 1)
litreview_ft_political_analysis <- lit_review_alt %>%
      flextable::as_flextable() %>%

@@

#https://cran.r-project.org/web/packages/ftExtra/vignettes/format_columns.html
#litreview_ft_political_analysis

#litreview_ft_political_analysis  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/litreview_ft_political_analysis.Rds'))
litreview_ft_political_analysis %>% 
    flextable::set_caption(caption = "Ontological coverage of ICBe versus existing State of the Art") %>%
   flextable::flextable_to_rmd()

# Uncomment for snapshot
# litreview_ft_political_analysis %>% 
#     #flextable::flextable_to_rmd()
#     save_as_image(path=here::here("replication_paper", "political_analysis_draft", "litreview_ft.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"

@@

ft   %>% 
    #flextable::flextable_to_rmd()
    save_as_image(path=here::here("replication_paper", "political_analysis_draft", "case_study_cuban_recall.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"

@@

ft   %>% 
    #flextable::flextable_to_rmd()
    save_as_image(path=here::here("replication_paper", "political_analysis_draft", "case_study_crimea_recall.png"),
                  zoom=1, webshot = "webshot2") # webshot = "webshot2"
```

@@

ft   %>% 
    #flextable::flextable_to_rmd()
    save_as_image(path=here::here("replication_paper", "political_analysis_draft", "recall_cuban_and_crimea.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"

@@

ggsave(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_recall.png'),
       plot = p_recall ,
       width=5, height=3.0)

@@

tiger <- image_read(here::here("replication_paper", "political_analysis_draft", "recall_cuban_and_crimea.png"))
tiger2 <- image_read(paste0(here::here(), '/replication_paper/political_analysis_draft/p_recall.png'))

combined <- image_composite(tiger, image_scale(tiger2, "x290"), offset = "+475+650")
image_write(combined, here::here("replication_paper", "political_analysis_draft", "recall_cuban_and_crimea_andcounts.png"))

@@

ratio=.75
height=18
save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_196_icbe.png'),
          p_196_icbe, base_height = 18, base_width = height*ratio)

@@

ratio=.75
height=18
save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_471_icbe.png'),
          p_471_icbe, base_height = 18, base_width = height*ratio)

@@

ratio=1.5
height=18
save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_precision_combined.png'),
          p_precision_combined, base_height = 18, base_width = height*ratio)

@@

ggsave(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=12, height=8)

@@

ggsave(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_dendro.png'), plot = p_dendro, width=12, height=10)

@@

ggsave(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_semantic_embeddings_dendro.png'), plot = p_combined, width=12, height=10)

@@

save_plot(file=paste0(here::here(),
                      '/replication_paper/political_analysis_draft/p_precision_icews.png'),
          p_ICEWS, base_height = 10, base_width = 14)

>>>>

ft_cuba_precision %>% save_as_image(path=here::here("replication_paper","psrm_draft","case_study_cuban_precision.png"), zoom=1) # webshot = "webshot2"
temp <- NULL

@@

bands=which( 1:nrow(lit_review_alt) %% 2 == 1)
litreview_ft_psrm <- lit_review_alt %>%
      flextable::as_flextable() %>%

@@

#https://cran.r-project.org/web/packages/ftExtra/vignettes/format_columns.html
#litreview_ft_psrm

#litreview_ft_psrm  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/litreview_ft_psrm.Rds'))
litreview_ft_psrm %>% 
    flextable::set_caption(caption = "Ontological coverage of ICBe versus existing State of the Art") %>%
   flextable::flextable_to_rmd()

# Uncomment for snapshot
# litreview_ft_psrm %>% 
#     #flextable::flextable_to_rmd()
#     save_as_image(path=here::here("replication_paper", "psrm_draft", "litreview_ft.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"

@@

ft   %>% 
    #flextable::flextable_to_rmd()
    save_as_image(path=here::here("replication_paper", "psrm_draft", "case_study_cuban_recall.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"

@@

ft   %>% 
    #flextable::flextable_to_rmd()
    save_as_image(path=here::here("replication_paper", "psrm_draft", "case_study_crimea_recall.png"),
                  zoom=1, webshot = "webshot2") # webshot = "webshot2"
```

@@

ft   %>% 
    #flextable::flextable_to_rmd()
    save_as_image(path=here::here("replication_paper", "psrm_draft", "recall_cuban_and_crimea.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"

@@

ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_recall.png'),
       plot = p_recall ,
       width=5, height=3.0)

@@

tiger <- image_read(here::here("replication_paper", "psrm_draft", "recall_cuban_and_crimea.png"))
tiger2 <- image_read(paste0(here::here(), '/replication_paper/psrm_draft/p_recall.png'))

combined <- image_composite(tiger, image_scale(tiger2, "x290"), offset = "+475+650")
image_write(combined, here::here("replication_paper", "psrm_draft", "recall_cuban_and_crimea_andcounts.png"))

@@

ratio=.75
height=18
save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_196_icbe.png'),
          p_196_icbe, base_height = 18, base_width = height*ratio)

@@

ratio=.75
height=18
save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_471_icbe.png'),
          p_471_icbe, base_height = 18, base_width = height*ratio)

@@

ratio=1.5
height=18
save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_precision_combined.png'),
          p_precision_combined, base_height = 18, base_width = height*ratio)

@@

ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=12, height=8)

@@

ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_dendro.png'), plot = p_dendro, width=12, height=10)

@@

ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_semantic_embeddings_dendro.png'), plot = p_combined, width=12, height=10)

@@

save_plot(file=paste0(here::here(),
                      '/replication_paper/psrm_draft/p_precision_icews.png'),
          p_ICEWS, base_height = 10, base_width = 14)

### 2022-10-24 replication_paper/psrm_draft/ICBe_supplemental_information.Rmd
psrm prep

temp_all %>% ungroup() %>% filter(crisno %in% c(1:60) )  %>% convert_to_ft() %>%
  save_as_image(path=here::here("replication_paper", "political_analysis_draft", "crisis_text_counts_ft1.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(61:120) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "political_analysis_draft", "crisis_text_counts_ft2.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(121:180) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "political_analysis_draft", "crisis_text_counts_ft3.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(181:240) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "political_analysis_draft", "crisis_text_counts_ft4.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(241:300) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "political_analysis_draft", "crisis_text_counts_ft5.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(301:360) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "political_analysis_draft", "crisis_text_counts_ft6.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(361:420) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "political_analysis_draft", "crisis_text_counts_ft7.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(421:480) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "political_analysis_draft", "crisis_text_counts_ft8.png"), zoom=1)

@@

  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_percent_chose_tag_by_concept.png'), 
                  plot = p_percent_chose_tag_by_concept, width=8, height=8)
}

@@

  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_percent_chose_tag_by_confidence.png'), 
                  plot = p_percent_chose_tag_by_confidence, width=8, height=6)
}

@@

ft_cuba_recall %>% save_as_image(path=here::here("replication_paper", "political_analysis_draft", "ft_cuba_recall.png"), zoom=1) # webshot = "webshot2"

@@

ft_crimea_recall %>% save_as_image(path=here::here("replication_paper", "political_analysis_draft", "ft_crimea_recall.png"), zoom=1) # webshot = "webshot2"

@@

  ft_crimea_precision_part1 %>% save_as_image(path=here::here("replication_paper", "political_analysis_draft", "case_study_crimea_precision_part1.png"), zoom=1) # webshot = "webshot2"

@@

  ft_crimea_precision_part2 %>% save_as_image(path=here::here("replication_paper", "political_analysis_draft", "case_study_crimea_precision_part2.png"), zoom=1) # webshot = "webshot2"

@@

ft_sample_precision_precision1 %>% save_as_image(path=here::here("replication_paper", "political_analysis_draft", "ft_sample_precision_precision1.png"), zoom=1) #

@@

ft_sample_precision_precision2 %>% save_as_image(path=here::here("replication_paper", "political_analysis_draft", "ft_sample_precision_precision2.png"), zoom=1) #

@@

ft_sample_precision_precision3 %>% save_as_image(path=here::here("replication_paper", "political_analysis_draft", "ft_sample_precision_precision3.png"), zoom=1) #

@@

ft_sample_precision_precision4 %>% save_as_image(path=here::here("replication_paper", "political_analysis_draft", "ft_sample_precision_precision4.png"), zoom=1) #

@@

    print(thiscrisis)
    save_icb_file <- paste0(here::here(), "/replication_paper/political_analysis_draft/p_icb_metro_plot_",thiscrisis,".Rds")

@@

  print(thiscrisis)
  #thiscrisis=471
  plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  save_mids_file <- paste0(here::here(), "/replication_paper/political_analysis_draft/p_mids_metro_plot_",thiscrisis,".Rds")

@@

    print(thiscrisis)
    plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
    save_file_penta <- paste0(here::here(), "/replication_paper/political_analysis_draft/p_phoenix_plot_penta_",thiscrisis,".Rds")
    save_file_lv0 <- paste0(here::here(), "/replication_paper/political_analysis_draft/p_phoenix_plot_lv0_",thiscrisis,".Rds")

@@

    print(thiscrisis)
    plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
    save_file_penta <- paste0(here::here(), "/replication_paper/political_analysis_draft/p_terrier_plot_penta_",thiscrisis,".Rds")
    save_file_lv0 <- paste0(here::here(), "/replication_paper/political_analysis_draft/p_terrier_plot_lv0_",thiscrisis,".Rds")

@@

    print(thiscrisis)
    plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
    save_file_penta <- paste0(here::here(), "/replication_paper/political_analysis_draft/p_icews_plot_penta_",thiscrisis,".Rds")
    save_file_lv0 <- paste0(here::here(), "/replication_paper/political_analysis_draft/p_icews_plot_lv0_",thiscrisis,".Rds")

@@

## Dyadic ICB
save_file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_icb_metro_plot_196.Rds')
p_metro_plot <- readRDS(save_file)
actor_colors <- p_metro_plot$actor_colors
subtitle="ICB Dyadic Events"
caption=paste0("Data: Dyadic International Crisis Behavior (ICB) (Hewitt 2003)
             ", p_metro_plot$labels$caption) #tag original to bottom

@@

save_file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_icb_metro_plot_196.Rds')
p_metro_plot <- readRDS(save_file)
p_196_phoenix <- p_metro_plot +
           theme(plot.margin=unit(c(0,0,0,0),"in")) +
  labs(
    #title = plot_title ,
    #subtitle = subtitle ,
    #caption = caption
  )

## MIDs
library(ggplot2)
save_file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_mids_metro_plot_196.Rds') 
p_metro_plot <- readRDS(save_file)
actor_colors <- p_metro_plot$actor_colors
subtitle="Dyadic Militarized Interstate Disputes (MIDs)"
caption=paste0("Source: CrisisEvents.org (Douglass et al. 2021)
                Data: Dyadic Militarized Interstate Disputes (MIDs) (Maoz et al. 2019)
             ", p_metro_plot$labels$caption
             ) #tag original to bottom
p_196_mids <- p_metro_plot +
           theme(plot.margin=unit(c(0,0,0,0),"in")) +
  labs(
    #title = plot_title ,
    #subtitle = subtitle ,
    #caption = caption
  ) 
#ggsave(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_mids_metro_plot_196.png'),
#       plot = p_metro_plot ,
#       width=12, height=14)

## Phoenix Crisis Map
#ICBe  196
library(ggplot2)
save_file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_phoenix_plot_penta_196.Rds')
subtitle="Phoenix Dyadic Events"
caption=paste0("Data: Cline Center Historical Phoenix Event Data (Althaus et al. 2017)
             ", p_metro_plot$labels$caption) #tag original to bottom

p_196_phoenix <- readRDS(save_file) +
    labs(
      #title = plot_title ,
      #subtitle = subtitle ,
      #caption = caption
    )
#ggsave(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_phoenix_metro_plot_196.png'),
#       plot = p_metro_plot ,
#       width=12, height=14)

@@

save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_196_combined.png'),
          p_196_combined, base_height = 12, base_width = 20)
#I'm just going to rotate on disk and load it as a normal figure
#\begin{sidewaysfigure}[H] #can't trust sideways plots either so have to rate the image
}
```

@@

if(fromscratch){
  p_phoenix_plot_lv0_196 <- readRDS(here::here("replication_paper", "political_analysis_draft", "p_phoenix_plot_lv0_196.Rds"))
  save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_phoenix_plot_lv0_196.png'),
            p_phoenix_plot_lv0_196 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
}
```

@@

## MIDs
library(ggplot2)
save_file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_mids_metro_plot_471.Rds') 
p_metro_plot <- readRDS(save_file)
actor_colors <- p_metro_plot$actor_colors
subtitle="Dyadic Militarized Interstate Disputes (MIDs)"
caption=paste0("Source: CrisisEvents.org (Douglass et al. 2021)
                Data: Dyadic Militarized Interstate Disputes (MIDs) (Maoz et al. 2019)
             ", p_metro_plot$labels$caption
             ) #tag original to bottom
p_471_mids <- p_metro_plot +
           theme(plot.margin=unit(c(0,0,0,0),"in")) +
  labs(
    #title = plot_title ,
    #subtitle = subtitle ,
    #caption = caption
  ) 
#ggsave(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_mids_metro_plot_196.png'),
#       plot = p_metro_plot ,
#       width=12, height=14)

## Phoenix Crisis Map
#ICBe  196
library(ggplot2)
save_file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_phoenix_plot_penta_471.Rds')
subtitle="Phoenix Dyadic Events"
caption=paste0("Data: Cline Center Historical Phoenix Event Data (Althaus et al. 2017)
             ", p_metro_plot$labels$caption) #tag original to bottom

p_471_phoenix <- readRDS(save_file) +
    labs(
      #title = plot_title ,
      #subtitle = subtitle ,
      #caption = caption
    )
#ggsave(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_phoenix_metro_plot_196.png'),
#       plot = p_metro_plot ,
#       width=12, height=14)

save_file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_terrier_plot_penta_471.Rds')
subtitle="Terrier Dyadic Events"
caption=paste0("Data: Terrier (Grant et al. 2021)
             ", p_metro_plot$labels$caption) #tag original to bottom

@@

save_file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_icews_plot_penta_471.Rds')
p_471_icews <- readRDS(save_file)

save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_471_mids.png'),
          p_471_mids, base_height = 18, base_width = 13.5)

@@

save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_471_combined.png'),
          p_471_combined, base_height = 14, base_width = 23)
}

@@

if(fromscratch){
  p_phoenix_plot_lv0_471 <- readRDS(here::here("replication_paper", "political_analysis_draft", "p_phoenix_plot_lv0_471.Rds"))
  save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_phoenix_plot_lv0_471.png'),
            p_phoenix_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
}
```

@@

if(fromscratch){
  p_terrier_plot_lv0_471 <- readRDS(here::here("replication_paper", "political_analysis_draft", "p_terrier_plot_lv0_471.Rds"))
  save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_terrier_plot_lv0_471.png'),
            p_terrier_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
}
```

@@

if(fromscratch){
  p_icews_plot_lv0_471 <- readRDS(here::here("replication_paper", "political_analysis_draft", "p_icews_plot_lv0_471.Rds"))
  save_plot(file=paste0(here::here(), '/replication_paper/political_analysis_draft/p_icews_plot_lv0_471.png'),
            p_icews_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
}
```

>>>>

temp_all %>% ungroup() %>% filter(crisno %in% c(1:60) )  %>% convert_to_ft() %>%
  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft1.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(61:120) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft2.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(121:180) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft3.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(181:240) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft4.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(241:300) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft5.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(301:360) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft6.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(361:420) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft7.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(421:480) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft8.png"), zoom=1)

@@

  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_percent_chose_tag_by_concept.png'), 
                  plot = p_percent_chose_tag_by_concept, width=8, height=8)
}

@@

  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_percent_chose_tag_by_confidence.png'), 
                  plot = p_percent_chose_tag_by_confidence, width=8, height=6)
}

@@

ft_cuba_recall %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "ft_cuba_recall.png"), zoom=1) # webshot = "webshot2"

@@

ft_crimea_recall %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "ft_crimea_recall.png"), zoom=1) # webshot = "webshot2"

@@

  ft_crimea_precision_part1 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "case_study_crimea_precision_part1.png"), zoom=1) # webshot = "webshot2"

@@

  ft_crimea_precision_part2 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "case_study_crimea_precision_part2.png"), zoom=1) # webshot = "webshot2"

@@

ft_sample_precision_precision1 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "ft_sample_precision_precision1.png"), zoom=1) #

@@

ft_sample_precision_precision2 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "ft_sample_precision_precision2.png"), zoom=1) #

@@

ft_sample_precision_precision3 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "ft_sample_precision_precision3.png"), zoom=1) #

@@

ft_sample_precision_precision4 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "ft_sample_precision_precision4.png"), zoom=1) #

@@

    print(thiscrisis)
    save_icb_file <- paste0(here::here(), "/replication_paper/psrm_draft/p_icb_metro_plot_",thiscrisis,".Rds")

@@

  print(thiscrisis)
  #thiscrisis=471
  plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  save_mids_file <- paste0(here::here(), "/replication_paper/psrm_draft/p_mids_metro_plot_",thiscrisis,".Rds")

@@

    print(thiscrisis)
    plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
    save_file_penta <- paste0(here::here(), "/replication_paper/psrm_draft/p_phoenix_plot_penta_",thiscrisis,".Rds")
    save_file_lv0 <- paste0(here::here(), "/replication_paper/psrm_draft/p_phoenix_plot_lv0_",thiscrisis,".Rds")

@@

    print(thiscrisis)
    plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
    save_file_penta <- paste0(here::here(), "/replication_paper/psrm_draft/p_terrier_plot_penta_",thiscrisis,".Rds")
    save_file_lv0 <- paste0(here::here(), "/replication_paper/psrm_draft/p_terrier_plot_lv0_",thiscrisis,".Rds")

@@

    print(thiscrisis)
    plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
    save_file_penta <- paste0(here::here(), "/replication_paper/psrm_draft/p_icews_plot_penta_",thiscrisis,".Rds")
    save_file_lv0 <- paste0(here::here(), "/replication_paper/psrm_draft/p_icews_plot_lv0_",thiscrisis,".Rds")

@@

## Dyadic ICB
save_file=paste0(here::here(), '/replication_paper/psrm_draft/p_icb_metro_plot_196.Rds')
p_metro_plot <- readRDS(save_file)
actor_colors <- p_metro_plot$actor_colors
subtitle="ICB Dyadic Events"
caption=paste0("Data: Dyadic International Crisis Behavior (ICB) (Hewitt 2003)
             ", p_metro_plot$labels$caption) #tag original to bottom

@@

save_file=paste0(here::here(), '/replication_paper/psrm_draft/p_icb_metro_plot_196.Rds')
p_metro_plot <- readRDS(save_file)
p_196_phoenix <- p_metro_plot +
           theme(plot.margin=unit(c(0,0,0,0),"in")) +
  labs(
    #title = plot_title ,
    #subtitle = subtitle ,
    #caption = caption
  )

## MIDs
library(ggplot2)
save_file=paste0(here::here(), '/replication_paper/psrm_draft/p_mids_metro_plot_196.Rds') 
p_metro_plot <- readRDS(save_file)
actor_colors <- p_metro_plot$actor_colors
subtitle="Dyadic Militarized Interstate Disputes (MIDs)"
caption=paste0("Source: CrisisEvents.org (Douglass et al. 2021)
                Data: Dyadic Militarized Interstate Disputes (MIDs) (Maoz et al. 2019)
             ", p_metro_plot$labels$caption
             ) #tag original to bottom
p_196_mids <- p_metro_plot +
           theme(plot.margin=unit(c(0,0,0,0),"in")) +
  labs(
    #title = plot_title ,
    #subtitle = subtitle ,
    #caption = caption
  ) 
#ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_mids_metro_plot_196.png'),
#       plot = p_metro_plot ,
#       width=12, height=14)

## Phoenix Crisis Map
#ICBe  196
library(ggplot2)
save_file=paste0(here::here(), '/replication_paper/psrm_draft/p_phoenix_plot_penta_196.Rds')
subtitle="Phoenix Dyadic Events"
caption=paste0("Data: Cline Center Historical Phoenix Event Data (Althaus et al. 2017)
             ", p_metro_plot$labels$caption) #tag original to bottom

p_196_phoenix <- readRDS(save_file) +
    labs(
      #title = plot_title ,
      #subtitle = subtitle ,
      #caption = caption
    )
#ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_phoenix_metro_plot_196.png'),
#       plot = p_metro_plot ,
#       width=12, height=14)

@@

save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_196_combined.png'),
          p_196_combined, base_height = 12, base_width = 20)
#I'm just going to rotate on disk and load it as a normal figure
#\begin{sidewaysfigure}[H] #can't trust sideways plots either so have to rate the image
}
```

@@

if(fromscratch){
  p_phoenix_plot_lv0_196 <- readRDS(here::here("replication_paper", "psrm_draft", "p_phoenix_plot_lv0_196.Rds"))
  save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_phoenix_plot_lv0_196.png'),
            p_phoenix_plot_lv0_196 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
}
```

@@

## MIDs
library(ggplot2)
save_file=paste0(here::here(), '/replication_paper/psrm_draft/p_mids_metro_plot_471.Rds') 
p_metro_plot <- readRDS(save_file)
actor_colors <- p_metro_plot$actor_colors
subtitle="Dyadic Militarized Interstate Disputes (MIDs)"
caption=paste0("Source: CrisisEvents.org (Douglass et al. 2021)
                Data: Dyadic Militarized Interstate Disputes (MIDs) (Maoz et al. 2019)
             ", p_metro_plot$labels$caption
             ) #tag original to bottom
p_471_mids <- p_metro_plot +
           theme(plot.margin=unit(c(0,0,0,0),"in")) +
  labs(
    #title = plot_title ,
    #subtitle = subtitle ,
    #caption = caption
  ) 
#ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_mids_metro_plot_196.png'),
#       plot = p_metro_plot ,
#       width=12, height=14)

## Phoenix Crisis Map
#ICBe  196
library(ggplot2)
save_file=paste0(here::here(), '/replication_paper/psrm_draft/p_phoenix_plot_penta_471.Rds')
subtitle="Phoenix Dyadic Events"
caption=paste0("Data: Cline Center Historical Phoenix Event Data (Althaus et al. 2017)
             ", p_metro_plot$labels$caption) #tag original to bottom

p_471_phoenix <- readRDS(save_file) +
    labs(
      #title = plot_title ,
      #subtitle = subtitle ,
      #caption = caption
    )
#ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_phoenix_metro_plot_196.png'),
#       plot = p_metro_plot ,
#       width=12, height=14)

save_file=paste0(here::here(), '/replication_paper/psrm_draft/p_terrier_plot_penta_471.Rds')
subtitle="Terrier Dyadic Events"
caption=paste0("Data: Terrier (Grant et al. 2021)
             ", p_metro_plot$labels$caption) #tag original to bottom

@@

save_file=paste0(here::here(), '/replication_paper/psrm_draft/p_icews_plot_penta_471.Rds')
p_471_icews <- readRDS(save_file)

save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_471_mids.png'),
          p_471_mids, base_height = 18, base_width = 13.5)

@@

save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_471_combined.png'),
          p_471_combined, base_height = 14, base_width = 23)
}

@@

if(fromscratch){
  p_phoenix_plot_lv0_471 <- readRDS(here::here("replication_paper", "psrm_draft", "p_phoenix_plot_lv0_471.Rds"))
  save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_phoenix_plot_lv0_471.png'),
            p_phoenix_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
}
```

@@

if(fromscratch){
  p_terrier_plot_lv0_471 <- readRDS(here::here("replication_paper", "psrm_draft", "p_terrier_plot_lv0_471.Rds"))
  save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_terrier_plot_lv0_471.png'),
            p_terrier_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
}
```

@@

if(fromscratch){
  p_icews_plot_lv0_471 <- readRDS(here::here("replication_paper", "psrm_draft", "p_icews_plot_lv0_471.Rds"))
  save_plot(file=paste0(here::here(), '/replication_paper/psrm_draft/p_icews_plot_lv0_471.png'),
            p_icews_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
}
```
